\section{Project Information}
\begin{itemize}
  \item \textbf{Name:} Decision Tree Classifier using Scikit-learn.
  \item \textbf{Developing Environment:} Visual Studio Code (Windows, WSL).
  \item \textbf{Programming Language:} Python.
  \item \textbf{Libraries and Tools:}
        \begin{itemize}
          \item \textbf{Libraries:}
                \begin{itemize}
                  \item \href{https://scikit-learn.org/stable/}{\textbf{scikit-learn:}} Machine learning library for training and evaluating decision tree models.
                  \item \href{https://pandas.pydata.org/}{\textbf{pandas:}} Data manipulation and analysis.
                  \item \href{https://numpy.org/}{\textbf{numpy:}} Numerical operations.
                  \item \href{https://matplotlib.org/}{\textbf{matplotlib}}, \href{https://seaborn.pydata.org/}{\textbf{seaborn:}} Data visualization libraries.
                  \item \href{https://graphviz.org/}{\textbf{graphviz:}} Visualization of decision trees.
                \end{itemize}
          \item \textbf{Tools:}
                \begin{itemize}
                  \item \href{https://git-scm.com/}{\textbf{Git}}, \href{https://github.com/}{\textbf{GitHub}}: Source code version control.
                  \item \href{https://code.visualstudio.com/}{\textbf{Visual Studio Code}}: Code editor for Python, LaTeX.
                \end{itemize}
        \end{itemize}
  \item \textbf{Datasets:}
        \begin{itemize}
          \item \href{https://archive.ics.uci.edu/dataset/17/breast+cancer+wisconsin+diagnostic}{\textbf{Breast Cancer Wisconsin (Diagnostic)}}
          \item \href{https://archive.ics.uci.edu/dataset/186/wine+quality}{\textbf{Wine Quality}}
          \item \href{https://archive.ics.uci.edu/dataset/19/car+evaluation}{\textbf{Car Evaluation}}
        \end{itemize}
\end{itemize}
